Project Setup

### 2024-09-09 choose_license.qmd
Use `pak` to calculate the dependencies

```r
direct_deps <- unique(renv::dependencies()$Package)
all_deps <- tools::package_dependencies(
  packages = direct_deps,
  which = "strong",
  recursive = TRUE
) |>
  unlist() |>
  append(deps) |>
  unique()
unique(installed.packages(fields = "License")[pkgs, "License"])
```
:::

>>>>

```r
deps <- renv::dependencies()$Package |>
  unique() |>
  pak::pkg_deps(dependencies = NA) |>
  getElement("package")
unique(installed.packages(fields="License")[deps, "License"])
```
:::

### 2024-09-09 setup.qmd
Use `pak` to calculate the dependencies

- __Think twice about your dependencies.__ Every dependency increases the risk of irreproducibility in the future. Prefer packages that are well-maintained and light on dependencies^[You can use the [R package dependency badges](https://tinyverse.netlify.app/) to count the direct and total dependencies.]. We also recommend you to read "When should you take a dependency?" by @Wickham2023PackagesDependency.

>>>>

- __Think twice about your dependencies.__ Every dependency increases the risk of irreproducibility in the future. Prefer packages that are well-maintained and light on dependencies^[You can use the function `pak::pkg_deps()` to count the total number of package dependencies in R.]. We also recommend you to read "When should you take a dependency?" by @Wickham2023PackagesDependency.
